Horse Racing Analysis

### 2023-12-15 analysis/new_analysis.qmd
wee typo fixed
contrast coding for .5 missing a period, now all results converge

df_ready <- df_ready |> mutate(delivery=factor(delivery,levels=c('fluent','disfluent')),
       speaker=factor(speaker)) # native comes before non
contrasts(df_ready$delivery) <- c(-.5,5)
contrasts(df_ready$speaker) <- c(-.5,5)
```

>>>>

df_ready <- df_ready |> mutate(delivery=factor(delivery,levels=c('fluent','disfluent')),
       speaker=factor(speaker)) # native comes before non
contrasts(df_ready$delivery) <- c(-.5,.5)
contrasts(df_ready$speaker) <- c(-.5,.5)
```
